systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-25 paper/trunk/systemfit_intro.tex
small edits by jeff so that it reads better
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@629 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Many theoretical models that are econometrically estimated
consist of more than one equation.
In this case, the disturbance terms of these equations are likely
to be contemporaneously correlated,
because some unconsidered factors
that influence the disturbance term in one equation
probably influence the disturbance terms in other equations
of this model, too.
Ignoring this contemporaneous correlation
and estimating these equations separately
leads to inefficient parameter estimates.
However, estimating all equations simultaneously,
taking the covariance structure of the residuals into account,
leads to efficient estimates.
This estimation procedure is generally called
°Seemingly Unrelated Regression° (SUR) \citep{zellner62}.
Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions.%
\footnote{
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).
}
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.

Furthermore, these models can contain variables
that appear on the left-hand side in one equation
and on the right-hand side of another equation.
Ignoring the endogeneity of these variables can lead to inconsistent
parameter estimates.
This simultaneity bias can be circumvented by applying
a °Two-Stage Least Squares° (2SLS) or °Three-Stage Least Squares° (3SLS)
estimation of the equation system.

@@

This paper is organized as follows:
In the following Section~\ref{sec:statistics} we
introduce the statistical background of estimating equation systems.
The implementation of the statistical procedures in \proglang{R}
is shortly explained in Section~\ref{sec:code}.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit} and especially how the features presented in the previous
section can be used.
In Section~\ref{sec:reliability} the reliability of the results from
\pkg{systemfit} are tested.
Finally, a summary and outlook are presented in
Section~\ref{sec:Summmary}.

>>>>

Many theoretical models that are econometrically estimated
consist of more than one equation.
The disturbance terms of these equations are likely
to be contemporaneously correlated,
because unconsidered factors
that influence the disturbance term in one equation
probably influence the disturbance terms in other equations.
Ignoring this contemporaneous correlation
and estimating these equations separately
leads to inefficient parameter estimates.
However, estimating all equations simultaneously,
taking the covariance structure of the residuals into account,
leads to efficient estimates.
This estimation procedure is generally called
"Seemingly Unrelated Regression" (SUR) \citep{zellner62}.
Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions.%
\footnote{
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).
}
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.

Furthermore, these models can contain variables
that appear on the left-hand side in one equation
and on the right-hand side of another equation.
Ignoring the endogeneity of these variables can lead to inconsistent
parameter estimates.
This simultaneity bias can be corrected for in each equation by
applying a "Two-Stage Least Squares" (2SLS) method or for all
equations simultaneously when combined with SUR resulting in a
"Three-Stage Least Squares" (3SLS) estimation of the system of
equations.

@@

% This paper is organized as follows:
In Section~\ref{sec:statistics} we introduce the statistical
background of estimating equation systems.
The implementation of the statistical procedures in \proglang{R} is
shortly explained in Section~\ref{sec:code}.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit} and how some of the features presented in the previous
section can be utilized.
In Section~\ref{sec:reliability} the reliability of the results from
\pkg{systemfit} are presented.
Finally, a summary and outlook are presented in
Section~\ref{sec:Summmary}.
